### 2018-02-01 polarization/paper.tex
very little left

	Abstract goes here

@@

	In this experiment, \textbf{TODO}.

@@

	This experiment verified Malus's law, \eqMalusLaw, for arrangements of two and three polarizers. In the former case, the laser, two polarizers (one with a rotary motion sensor) and the detector were setup such that maximum amount of light was allowed through without oversaturating the detector. Collecting intensity measurements involved unifromly rotating the polarizer with the rotary motion sensor through \( 180 \si{\degree} \). Data was collected using provided \textit{Polarization of Light} software.

	To verify Malus's law for three polarizers, two polarizers were initially arranged to achieve maximum intensity of transmitted light. Furter, a third polarizer with a rotary motion sensor was inserted between the two initial polarizers and rotated to obtain a minimum in the intensity of transmitted light. Intensity measurements were collected through \( 360 \si{\degree} \) using the provided software.

	The experimental arrangements for investigating polarization of light by reflection involved an acrylic semi-circular lens, a polarizer mounted on the optical bench, a spectrophotometer table with a rotary motion sensor and an optional square polarizer to be mounter on the spectrophotometer table. Furhter, a set of collimating slits was used for focusing the light beam. To calibrate the setup, \textbf{TODO}. The optical benches along with required optical elements are shown below \textbf{TODO}.

@@

	Intensity of light passing through two polarizers was measured as a function of position. Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm \)\textbf{TODO}. Obtained data is visualized below.
	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are included but are too small to be visible.}

	Further, intensity vs. position of the rotary motion sensor of the middle polarizer was measured for three polarizers. Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm \)\textbf{TODO} respectively.
	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are not included \textbf{TODO} explain why.}

	Finally, intensity vs. position data was collected for the experimental setup investigating polarization by reflection. Uncertainties were taken to be \textbf{TODO}. 
	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are not included \textbf{TODO} explain why.}

@@

	To begin with, Malus's law was verified using the obtained data for two polarizers. Fitting the measured intensity and angles to \( \cos \theta \) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \). Fitting the data to \eqMalusLaw instead (i.e. testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model. The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm 0.0008} \). A visualization of the fit along with residuals is shown below.
	\paperfig{Exercise1Fit}{\pdf{exercise1-model}}{Light intensity and and fit residuals plotted against the angular position of the sensor for the two polarizer setup. The curve in red has the function \( \pars{3.8269 \pm 0.0008} \cos ^ 2 \theta \); \( R ^ 2 \) value of the fit is \( 0.999548 \). Error bars were included but are too small to be visible.}

	Further, the data obtained for three polarizers was fit to \eqThreePolarizers using the least squares method. The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm 0.002} \si{\volt} \). Reduced \( \chi^2 \) was \( 3.422214 \); \( R^2 \) for this fit was \( 0.994677 \).
	\paperfig{Exercise2Fit}{\pdf{exercise2-model}}{Intensity of light exiting the third polarizer and fit residuals vs. the angular position of the second polarizer. The curve has the function \( \pars{2.891 \pm 0.002} \sin^2 \pars{2\phi} \). \( R^2 \) of this fit was \( 0.994677 \). Error bars are not included due to \textbf{TODO}.}

	\textbf{TODO} questions for exercise 2.

	To estimate the value of Brewster's angle \( \theta_p \), given by \eqPolarizingAngle, obtained experimental data for intensity of light vs. angular position of the sensor (\figExerciseThreeData) was filtered to include only the maximum intensity data points. A least squares fit on the obtained boundary points was then performed with a degree-7 polynomial as the model function.

	\textbf{TODO} include coefficients of polynomial, \( R^2 \), reduced \( \chi^2 \)

	\paperfig{ExerciseThreeFit}{\pdf{exercise3-model}}{Intensity of light vs. angular position of the sensor for rays reflected off acrylic semi-circular block. Curve in red is a degree-7 polynomial; data was filtered by taking the maximum-intensity data point in 300-point intervals.}

	\textbf{TODO} increase distance between plots to prevent ylabel from overlapping w/ left subplot.

@@

	Conclusion goes here

@@

\end{paper}
\end{document}

>>>>

	TODO Abstract

@@

@@

	This experiment verified Malus's law, \eqMalusLaw, for arrangements of two and three polarizers. In the former case, the laser, two polarizers (one with a rotary motion sensor) and the detector were setup such that maximum amount of light was allowed through without oversaturating the detector. Collecting intensity measurements involved uniformly rotating the polarizer with the rotary motion sensor through \( 180 \si{\degree} \). Data was collected using provided \textit{Polarization of Light} software.

	To verify Malus's law for three polarizers, two polarizers were initially arranged to achieve maximum intensity of transmitted light. Further, a third polarizer with a rotary motion sensor was inserted between the two initial polarizers and rotated to obtain a minimum in the intensity of transmitted light. Intensity measurements were collected through \( 360 \si{\degree} \) using the provided software.

	The experimental arrangements for investigating polarization of light by reflection involved an acrylic D-lens, a polarizer mounted on the optical bench, a spectrophotometer table with a rotary motion sensor and an optional square polarizer to be mounter on the spectrophotometer table. Further, a set of collimating slits was used for focusing the light beam. To calibrate the setup, the polarizers were carefully rotated to ensure that their alignment was exactly as required, in addition to comparing the values listed on the outside (such as aligning a polarizer with the label 0, in the case of a vertical polarizer). The optical benches along with required optical elements are shown below. The experiment was carried out by rotating the platform with the detector while simultaneously rotating the D-lens to keep the reflected beam aligned with the detector.

	\paperfig{Setup}{\pdf{setup}}{The setup used in the experiments.
	Along the top track are the three polarizers used in the second part of the experiment. For the first part of the experiment, the middle polarizer was removed. For the first two experiments, a light source was placed on the left of the top track, which shone into the light detector on the right of the top track. For the Brewster's angle experiment, the bottom track was used. The light source (bottom right corner) shone through a polarizer (bottom right), collimating slits (bottom middle), reflected off of the D-lens (bottom left), and was detected by the detector (middle left).}

@@

	Intensity of light passing through two polarizers was measured as a function of position. Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm .02\). Obtained data is visualized below.
	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are 3included but are too small to be visible.}

	Further, intensity vs. position of the rotary motion sensor of the middle polarizer was measured for three polarizers. Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm .02\) respectively.
	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are included but are too small to be visible.}

	Finally, intensity vs. position data was collected for the experimental setup investigating polarization by reflection. Uncertainties were taken to be \( \pm .01 \si{\volt} \) in intensity and \( \pm .02\) in position.
	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are included but are too small to be visible.}

@@

	To begin with, Malus's law was verified using the obtained data for two polarizers. Fitting the measured intensity and angles to \( \cos (\theta )\) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \). Fitting the data to \eqMalusLaw instead (i.e. testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model. The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm .0008} \). A visualization of the fit along with residuals is shown below.
	\paperfig{ExerciseOneFit}{\pdf{exercise1-model}}{Light intensity and fit residuals plotted against the angular position of the sensor for the two polarizer setup. The curve in red has the function \( \pars{3.8269 \pm .0008} \cos ^ 2( \theta )\); \( R ^ 2 \) value of the fit is \( 0.999548 \). Error bars were included but are too small to be visible.}

	Further, the data obtained for three polarizers was fit to \eqThreePolarizers using the least squares method. The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm .002} \si{\volt} \). Reduced \( \chi^2 \) was \( 3.422214 \); \( R^2 \) for this fit was \( 0.994677 \).
	\paperfig{ExerciseTwoFit}{\pdf{exercise2-model}}{Intensity of light exiting the third polarizer and fit residuals vs. the angular position of the second polarizer. The curve has the function \( \pars{2.891 \pm .002} \sin^2 \pars{2\phi} \). \( R^2 \) of this fit was \( 0.994677 \). Error bars are included but are too small to be visible.}

	The graph in \figExerciseTwoFit differs from the one in \figExerciseOneFit in two major ways. The first is that it has a frequency equal to double of the one in \figExerciseOneFit. The second is that it starts from a peak and descends, while the graph in \figExerciseOneFit does the opposite, by starting from a minimum.

	The maximum transmission through the three polarizers can be calculated by maximizing \eqThreePolarizers. The peak is attained when the first and middle polarizer are $\SI{45}{\degree}$ apart. From the same equation, it can be seen that the minimum transmission is obtained when the first and middle polarizers are either $\SI{0}{\degree}$ or $\SI{90}{\degree}$ apart.

	In the Brewster's angle experiment, the data was very noisy due to the fact that it is near impossible to rotate both the lens and the detector slowly while keeping the reflected light beam aligned with the detector. To estimate the value of Brewster's angle \( \theta_p \), given by \eqPolarizingAngle, obtained experimental data for intensity of light vs. angular position of the sensor (\figExerciseThreeData) was filtered to include only the maximum intensity data points, as those represented when the light beam was perfectly aligned with the detector. A least squares fit on the obtained boundary points was then performed with a cubic polynomial as the model function, which was deemed a good function to approximate the peak intensities of the data.

	This function was chosen not to model the curve, but to find the minimum of the dip. The fit was deemed a good approximation as it had a reduced $\chi^2$ value of 2.00305 and an $R^2$ value of 0.983524. By taking the minimum of the polynomial, Brewster's angle was found to be $54.0\pm.5$, which resulted in a refractive index of $1.38\pm.01$ for acrylic. All uncertainties were propagated using the method of quadratures.

	\paperfig{ExerciseThreeFit}{\hspace{-4ex}\scalebox{1.2}[1.2]{\pdf{exercise3-model}}}{Intensity of light vs sensor position for rays reflected off acrylic D-lens. Curve in red is a cubic polynomial; data was filtered by taking the maximum-intensity data point in 300-point intervals. The fit had an $R^2$ value of 0.983524. Error bars were included but were too small to be visible.}

@@

	TODO Conclusion

@@

\end{paper}

TODO PYTHON CODE
\end{document}
